%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref} % For hyperlinks
\hypersetup{
    colorlinks=true,  % Enable colored links
    linkcolor=black,  % Color of internal links
    citecolor=black,  % Color of citation links
    urlcolor=blue     % Color of external links
}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{NGUYEN NHAT TAN} % Your name
\address{District 12, Ho Chi Minh City} % Your address
\address{(+84) 858.111.879 \\ nguyennhattan.work@gmail.com \\ TanNguyen20.github.io} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EXECUTIVE SUMMARY & CAREER OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Executive Summary \& Career Objective}
As a Full Stack Developer with over 2 years of experience, I have a strong foundation in ReactJS, TypeScript, NextJS, and Java Spring Boot. My goal is to contribute to a dynamic company's success as a Full Stack Developer, continuously learning and improving to deliver effective solutions. I stay up-to-date with the latest software development technologies and best practices, striving to become a valuable asset to any team I join.
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
{\bf Full Stack Developer, TMA Solutions} \hfill {\em 07/2024 – Present}
\\ \textbf{Project: AI Automation Test System}
\\ \textbf{Team Size:} 8 members
\\ \textbf{Job overview and responsibilities:}
\begin{itemize}
    \item Utilized Azure OpenAI to generate test cases and execute them in real-time.
    \item Implemented WebSocket and Event Stream technology for real-time data \& real-time logging.
    \item Developed a hierarchical structure for managing test cases.
    \item Created an agent to run test cases and view test reports.
    \item Set up a deployment pipeline.
    \item Developed and implemented an integrated video recording system to capture test case execution.
\end{itemize}
\textbf{Technologies Used:}
\begin{itemize}
    \item \textbf{React (TypeScript):} Radix for theming, CodeMirror for the code editor
    \item \textbf{Java:} Spring Security, Spring WebSocket, Spring Oauth2, Spring JPA, Spring Actuator, Spring Mail, Schedule, Spring Data Redis, Spring Doc, Fasterxml Jackson(JSON library), JGit, Lombok, Gradle
    \item \textbf{Azure OpenAI:} For test case generation
    \item \textbf{WebSocket \& Event Stream:} For real-time data \& logging 
    \item \textbf{Python:} For automation scripts
    \item \textbf{Database:} SQL Server
    \item \textbf{Docker:} Set up agents for running test cases using Cypress, Selenium (Python, CSharp) and Playwright (Python)
    \item \textbf{DevOps:} Kubernetes, Linux Scripting, CI/CD pipelines with Azure DevOps
    \item \textbf{Code Quality and Analysis Tools:} Sonar, Checkstyle, Vitest, Junit, Mockito, Eslint, Prettier
\end{itemize}

\vspace{0.2cm} % Add some space before the next project

{\bf Full Stack Developer, TMA Solutions} \hfill {\em 04/2023 – 06/2024}
\\ \textbf{Project: Semantic Search}
\\ \textbf{Team Size:} 15 members
\\ \textbf{Job overview and responsibilities:}
\begin{itemize}
    \item Contributed to the design and development of semantic search features.
    \item Collaborated with cross-functional teams to implement new search algorithms.
    \item Integrated Azure AI Search and OpenAI to enhance semantic query capabilities.
    \item Developed and optimized data crawling solutions using Python and FastAPI.
    \item Set up a deployment pipeline.
\end{itemize}
\textbf{Technologies Used:}
\begin{itemize}
    \item \textbf{React (TypeScript):} Vite, Radix, Tailwind, React Hook Form, @stomp/stompjs (WebSocket), Axios, ESLint, Prettier, ag-grid-react, Husky, ChartJS
    \item \textbf{Java:} Spring Security, Spring Oauth2, Spring JPA, Spring WebSocket, Spring Data, Spring Data Redis, Spring Actuator, Spring Mail, Lombok, Spring Session, Spring Doc, Gradle
    \item \textbf{Azure Services:} Azure AI Search, Azure OpenAI, Redis, Azure Storage Account, SQL Server
    \item \textbf{Python:} FastAPI, Scrapy (Data Crawling), Playwright, WebSocket
    \item \textbf{Docker:} Setup agents to crawl data from a specific site
    \item \textbf{DevOps:} Kubernetes, Linux Scripting, CI/CD pipelines with Azure DevOps
    \item \textbf{Code Quality and Analysis Tools:} Sonar, Checkstyle, Vitest, Junit, Mockito, Eslint, Prettier
\end{itemize}

\vspace{0.2cm} % Add some space before the next project

{\bf Full Stack Developer, TMA Solutions} \hfill {\em 01/2022 – 03/2023} 
\\ \textbf{Project: DHP Eventbus}
\\ \textbf{Team Size:} 6 members
\\ \textbf{Job overview and responsibilities:}
\begin{itemize}
    \item Developed new features for existing projects.
    \item Maintained and supported existing features.
    \item Implemented unit tests for developed features.
    \item Configured infrastructure for deployment.
\end{itemize}
\textbf{Technologies Used:} 
\begin{itemize}
    \item \textbf{React (TypeScript):} Vite(migrate from create-react-app), Micro Frontend, Webpack, Antd, WebSocket (stompjs), Axios, ESLint, Prettier, Husky
    \item \textbf{Java:} Spring Web, Apache Pulsar, Spring JPA, Spring Clould Vault, Fasterxml Jackson (Json library), Spring security, Spring Mail, Spring Doc, Gradle
    \item \textbf{SQL Server:} Database management and optimization
    \item \textbf{DevOps:} Azure DevOps, Kubernetes, Docker
    \item \textbf{Testing:} Jest (UI testing), Mockito \& JUnit (Backend testing), Selenium (Automation testing)
    \item \textbf{Code Quality and Analysis Tools:} Sonar, Checkstyle, Junit, Mockito, Jest, Eslint, Prettier
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
{\bf Flow Chart App} \hfill {\em 06/2023 – Present}
\\ \textbf{Technologies Used:} NextJS, Next Auth, MUI, Java Spring Boot, Tailwind, PostgreSQL, Azure DevOps, Jest
\\ \textbf{Description:} An editor for building charts and diagrams.
\\ \textbf{Repo:} \href{https://dev.azure.com/nhattan1506/Public-Project/_git/flow-chart-app}{Flow Chart App} \\
\textbf{Website:} \href{https://tannguyen.id.vn}{tannguyen.id.vn}

\vspace{0.2cm} % Optional space between projects

{\bf A Management Software System for Car Care Service} \hfill {\em 08/2021 - 12/2021}
\\ \textbf{Technologies Used:} NodeJS, ReactJS, React Native, Socket.io, Bootstrap, MongoDB, Vnpay
\\ \textbf{Description:} A software system providing car care services, including appointment scheduling and payment integration.
\\ \textbf{Repo:} \href{https://github.com/OtoViet}{OtoViet}
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
{\bf Hard Skills}
\begin{itemize}
    \item ReactJS, Java Spring Boot, NextJS, NodeJS
    \item Antd, Material UI, Radix, ChartJS, Highcharts, React Ag-Grid
    \item Java (Spring Boot, Spring Security, Spring Data, Spring Oauth2, Schedule, Spring Data Redis, Spring Mail, Spring Actuator, Spring Clould, Lombok)
    \item HTML, CSS, JavaScript (ES6+), TypeScript, Responsive Design
    \item OAuth2, JWT for authentication and authorization
    \item Redis, Apache Pulsar, RabbitMQ
    \item Docker, Kubernetes, Azure Pipeline
    \item SQL Server, MongoDB, PostgreSQL
    \item Design patterns, Clean Code
    \item Sonar, Checkstyle, Gradle, Eslint, Prettier
\end{itemize}

{\bf Soft Skills}
\begin{itemize}
    \item Teamwork
    \item Agile, Kanban
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Can Tho University} \hfill {\em 09/2018 - 09/2022} 
\\ \textbf{Major:} Information Technology \hfill { GPA: 3.42/4 }
\end{rSection}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Achievements}
\begin{itemize}
    \item {\bf TMA Star Performers}: Recognized for outstanding contributions and performance at TMA Solutions.
\end{itemize}
\end{rSection}

\end{document}
